% SITCOM-679 Jira task
\documentclass[SE,authoryear,lsstdraft]{lsstdoc}
\input{meta}

% Package imports go here.
\usepackage{hyperref}
% Local commands go here.
%If you want glossaries
%\input{aglossary.tex}
%\makeglossaries

\title{FAFF Implementation Group (FIG) Mandate}

% Optional subtitle
% \setDocSubtitle{A subtitle}

\author{%
Scot Kleinman,
Tony Jounson,
and
Patrick Ingraham
}

\setDocRef{SITCOMTN-059}
\setDocUpstreamLocation{\url{https://github.com/lsst-sitcom/sitcomtn-059}}

\date{\vcsDate}

% Optional: name of the document's curator
% \setDocCurator{The Curator of this Document}

\setDocAbstract{%
The FIG (FAFF Implementation Group) exists to take the recommendations
of the FAFF reports
(\citeds{SITCOMTN-025} and \citeds{SITCOMTN-037})
and implement them. This document provides the group's mandate.
}

% Change history defined here.
% Order: oldest first.
% Fields: VERSION, DATE, DESCRIPTION, OWNER NAME.
% See LPM-51 for version number policy.
\setDocChangeRecord{%
  \addtohist{1}{2023-02-27}{Unreleased.}{Scot Kleinman}
}


\begin{document}

% Create the title page.
\maketitle
% Frequently for a technote we do not want a title page  uncomment this to remove the title page and changelog.
% use \mkshorttitle to remove the extra pages

% ADD CONTENT HERE XXX
% You can also use the \input command to include several content files.
\section{Scope}
The broad directive for the FAFF Implementation Group (FIG) is to
implement and deliver the project tools and other deliverables recommended
within the two First-Look Analysis and Feedback Functionality (FAFF)
Breakout Group reports, \citeds{SITCOMTN-025} and \citeds{SITCOMTN-037}.

\section{Timeline}
The FIG should complete and make its final deliverables within
approximately one year of project initiation.  The timeline should be
clearly described in the first deliverable described below.  This first
deliverable shall be due within eight weeks of project initiation. 
Completing work earlier is highly desirable.


\section{Sponsor}
Wil O’Mullane shall be the executive sponsor and the FIG leadership
team report to Wil O’Mullane.  The executive sponsor provides the project top management support and allocation of resources.
FIG leadership will also work with Robert Lupton and
Anastasia Alexov given the overlap of goals and
resources between their domains and the the FIG.



\section{Product owner}
Patrick Ingraham shall be the Product Owner.  As such, Patrick will
advise and consult with the group leadership, but not play an active
daily role in project management or implementation.  The product owner
helps establish project priorities and acceptable solutions.


\section{FIG leadership team}
Tony Johnson and Scot Kleinman shall lead the project from a technical
and managerial perspective respectively. They shall select a core team
to lead the project, subject to standard resource allocation practices. 


\section{Deliverables}
The FIG is responsible for two sets of deliverables. The first is a
single report that contains a full project roadmap that is responsive to
the FAFF report recommendations. This roadmap shall be responsive to the
recommendations and proposed requirements included in the two FAFF reports
with any key differences, omissions, and extensions clearly justified. 
The roadmap should contain an implementable plan with identified resources
to perform the needed work and preliminary approval from the resources
and their managers for their time.  The roadmap should clearly describe
the project scope and deliverables with a set of milestones and clear
priorities consistent with the timeline for delivery.  The roadmap will
likely need to identify a common framework for the proceeding work.  The
report should note areas of critical resource allocation and the risks
and rewards likely from changes to the proposed resource allocation. 
If some FAFF recommendations cannot be adequately addressed within the
timeline, the report should demonstrate how the FAFF-identified need
can get addressed both in the continued absence of resources and with
a specific amount of additional resources engaged in the work.  In the
event of other deviations that prevent completion of a planned activity,
the FIG should report to the Product Owner, then Sponsor and present a
suggested alternative path forward.


The second set of deliverables shall consist of those specified in the sponsor-approved roadmap contained within the first deliverable. 


\appendix
% Include all the relevant bib files.
% https://lsst-texmf.lsst.io/lsstdoc.html#bibliographies
%\section{References} \label{sec:bib}
%\renewcommand{\refname}{} % Suppress default Bibliography section
%\bibliography{local,lsst,lsst-dm,refs_ads,refs,books}

% Make sure lsst-texmf/bin/generateAcronyms.py is in your path
\section{Acronyms} \label{sec:acronyms}
\input{acronyms.tex}
% If you want glossary uncomment below -- comment out the two lines above
%\printglossaries





\end{document}
